Understanding the Landscape of Childlessness in the U.S.: A Data-Driven Exploration (1972-2022)

### 2024-03-11 outputs/paper/paper.qmd
Added the names of the contributors

---
title: "Understanding the Landscape of Childlessness in the U.S.: A Data-Driven Exploration (1972-2022)"
author: Mehrnoush Mohammadi & Quang Mai
thanks: "Code and data are available at: https://github.com/mehrnoush68/childlessness-in-america.git"
date: today
date-format: long
abstract: "This paper investigates trends in childlessness in the United States from 1972 to 2022. Data from the General Social Survey (GSS) is analyzed to consider factors like age, gender, education, class, health condition, marital status and number of children. The analysis reveals a consistent rise in childlessness across various demographics, potentially linked to economic considerations, educational attainment, and shifting social norms. The paper explores the potential social and economic implications of this trend, highlighting the need for further research to navigate the complexities surrounding childlessness in today's society."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

(@) Are you currently--married, widowed, divorced, separated, or have you never been married?:
- Married
- Widowed
- Divorced
- Separated
- Never married

(@) Would you say your own health, in general, is excellent, good, fair, or  poor?:
- Excellent
- Good
- Fair
- Poor

>>>>

---
title: "Understanding the Landscape of Childlessness in the U.S.: A Data-Driven Exploration (1972-2022)"
author: 
  - Mehrnoush Mohammadi 
  - Quang Mai
thanks: "Code and data are available at: https://github.com/mehrnoush68/childlessness-in-america.git"
date: today
date-format: long
abstract: "This paper investigates trends in childlessness in the United States from 1972 to 2022. Data from the General Social Survey (GSS) is analyzed to consider factors like age, gender, education, class, health condition, marital status and number of children. The analysis reveals a consistent rise in childlessness across various demographics, potentially linked to economic considerations, educational attainment, and shifting social norms. The paper explores the potential social and economic implications of this trend, highlighting the need for further research to navigate the complexities surrounding childlessness in today's society."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

(@) Are you currently:
- Married
- Widowed
- Divorced
- Separated
- Never married

(@) Would you say your own health, in general:
- Excellent
- Good
- Fair
- Poor
